Formal Verification of Real Models from Platforms Using The B-method

### 2009-04-28 papers/FM2009/source/paper.tex
Related works

 Others advantages of this work are the use of news and advanceds funcionalities of B method. Normaly, the related
 works don`t enjoy this funcionalities, because these are news and required advanced knowleadge about tools for B
 method. These advantages are the paralelization of prove proccess and the instensive use of math patterns
 associated with proof commands.

 [AMM]
Verificação formal já vem sendo aplicada com sucesso na verificação \ldots Porém os custos eram altos, pois se
passou X tempo para modelar \ldots e

@@

 \section{Conlusitions}

>>>>

 Others advantages of this work are the aplication of news and advanceds funcionalities of B method.
 These advantages are the paralelization of prove proccess and the instensive use of math patterns associated
 with proof commands. Normaly, the related works don`t enjoy this funcionalities, because these are news
 and required advanced knowleadge about tools for B method.

 [AMM]
 Adici \erro [ Adicionar aqui a comparação enviada ao e-mail de David]

Verificação formal já vem sendo aplicada com sucesso na verificação \ldots Porém os custos eram altos,
pois se passou X tempo para modelar \ldots e

@@

 \section{Conclusitions}
